Physical Chemistry Tips

### 2015-12-08 physical_chemistry/latex/pchem_tips.tex
blah

\begin{align*}
  \frac{\partial G}{\partial P}_T &= V\\
  \Delta \overline{G}_{ideal} &= \Delta G_{ideal}\degree + RT\ln\left(\frac{P}{P\degree}\right)\\
  \Delta \overline{G} &= \Delta G\degree + RT\ln\left(\frac{f}{P\degree}\right)\\
  \frac{f}{P} &= e^{\frac{1}{RT}\int_0^P(\bar{V}-\bar{V}^{id})dP} = e^{\int_0^P\frac{Z-1}{P}dP}\\
  \mu_i &= \mu_i\degree + RT\ln(a_i)\\
  \mu_i &= \mu_i\degree + RT\ln\left(\frac{f_i}{P\degree}\right)\\
\end{align*}

@@

\begin{align*}
  P_i &= \frac{n_iRT}{V} = C_iRT\\
  K_p &= \Pi \left(\frac{C_iRT}{P\degree}\right)^{\nu_i} = \left(\frac{C_i\degree RT}{P\degree}\right)^{\nu_i} \Pi \left(\frac{C_i}{C_i\degree}\right)^{\nu_i}\\
\end{align*}

\begin{align*}
  \mbox{Ideal gas expansion}&\hspace{2cm}\Delta S = R\ln(\frac{V_2}{V_1})\\
  \mbox{Ideal gas mixing}&\hspace{2cm}\Delta S = -R\sum y_i\ln(y_i)\\
  \mbox{Nonideal phase transition}&\hspace{2cm} \Delta S = \frac{\Delta H}{T}\\
\end{align*}

@@

\begin{align*}
  \mu_i = \mu_i\degree + RT\ln\left(\frac{P_i}{P\degree}\right)\\
  \overline{G}_i = \overline{G}_i\degree + RT\ln\left(\frac{P_i}{P\degree}\right)\\
\end{align*}

>>>>

\begin{align*}
  \frac{\partial G}{\partial P}_T &= V\\
  \Delta \overline{G}_{ideal} &= \Delta G_{ideal}\degree + RT\ln\left(\frac{P}{P\degree}\right)\\
  \Delta \overline{G} &= \Delta G\degree + RT\ln\left(\frac{f}{P\degree}\right)\\
  \frac{f}{P} &= e^{\frac{1}{RT}\int_0^P(\bar{V}-\bar{V}^{id})dP} = e^{\int_0^P\frac{Z-1}{P}dP}\\
  \mu_i &= \mu_i\degree + RT\ln(a_i) \hspace{2cm}\mbox{Activity ~ purity, caps at 1}\\
  &\mbox{Pure liquids have an activity of 1}\\
  \mu_i &= \mu_i\degree + RT\ln\left(\frac{f_i}{P\degree}\right)\\
\end{align*}

@@

\begin{align*}
  P_i &= \frac{n_iRT}{V} = C_iRT\\
  K_p &= \Pi \left(\frac{C_iRT}{P\degree}\right)^{\nu_i} = \left(\frac{C_i\degree RT}{P\degree}\right)^{\nu_i} \Pi \left(\frac{C_i}{C_i\degree}\right)^{\nu_i}\\
  K_c &= \Pi\left(\frac{c_i}{c\degree}\right)^{\nu_i}\\
  k &= \frac{c}{K}\\
\end{align*}

\begin{align*}
  V &= \frac{mRT}{MP}\\
  &\mbox{For dissociation A -> 2B}\\
  K &= \frac{4\xi^2}{1-\xi^2}\\
  \xi &= \frac{M_1-M_2}{M_2}\\
\end{align*}

\begin{align*}
  k &= e^{\frac{-\Delta G}{RT}}\\
\end{align*}

\begin{align*}
  \Delta_f G_{isomer} &= -RT\ln\left(\sum e^{\frac{-\Delta_f G_i}{RT}}\right)\\
  \Delta_f H_{isomer}\degree &= \sum r_i \Delta_f H_i\degree\\
  r_i &= e^{\frac{\Delta_f G_{isomer} - \Delta_f G_i}{RT}}\\
\end{align*}

\begin{align*}
  \mbox{Ideal gas expansion - isothermal?}&\hspace{2cm}\Delta S = R\ln(\frac{V_2}{V_1}) = R\ln(\frac{P_1}{P_2})\\
  \mbox{Ideal gas mixing}&\hspace{2cm}\Delta S = -R\sum y_i\ln(y_i)\\
  \mbox{Nonideal phase transition}&\hspace{2cm} \Delta S = \frac{\Delta H}{T}\\
  \mbox{Constant V heating}&\hspace{2cm} \Delta S = \int_{T1}^{T2} \frac{C_V}{T}dT\\
  \mbox{Constant P heating}&\hspace{2cm} \Delta S = \int_{T1}^{T2} \frac{C_P}{T}dT\\
  \mbox{Phase change constant T,P}&\hspace{2cm} \Delta S = \frac{\Delta H}{T}\\
\end{align*}

@@

\begin{align*}
  \mu_i &= \mu_i\degree + RT\ln\left(\frac{P_i}{P\degree}\right)\\
  \overline{G}_i &= \overline{G}_i\degree + RT\ln\left(\frac{P_i}{P\degree}\right)\\
  \Delta_r G &= \sum \nu_i\mu_i = \sum \nu_i \Delta_f G_i\\
\end{align*}

\begin{align*}
  \ln\left(\frac{K_2}{K_1}\right) &= \frac{\Delta_r H\degree(T_2-T_1)}{RT_1T_2}\\
\end{align*}

\begin{align*}
  \mbox{Clapeyron Equation}\\
  \frac{dP}{dT} &= \frac{\Delta S}{\Delta V} = \frac{\Delta H}{T\Delta V}\\
  a_i &= \frac{P_i}{P_i*}\hspace{2cm}\mbox{The activity is the vapor pressure over the pure vapor pressure}\\
  P_i &= x_iP_i*\hspace{2cm}\mbox{xi is mol frawction of i in liquid}\\
  a_i &= x_i\hspace{2cm}\mbox{Ideal solutions only}\\
  \mu_i(l) &= \mu_i(l)\degree + RT\ln(x_i)\hspace{2cm}\mbox{Ideal solutions only}\\
  P_i &= y_iP = K_ix_i\hspace{2cm}\mbox{Henry's law}\\
\end{align*}

\begin{align*}
  n_i &= nz_i = n_{\ell}x_i + n_{v}y_i\hspace{2cm}\mbox{x: solution fraction, y: vapor fraction}\\
  \frac{n_\ell}{n_v} &= \frac{z_i - y_i}{x_i - z_i}\hspace{2cm}\mbox{Lever rule, tells you liquid:gas, since z in between x and y}\\
  \mu_i &= \mu_i\degree + RT\ln(v_ix_i)\\
  v_i &= \frac{P_i}{x_iP_i*} = \frac{y_iP}{x_iP_i*}\hspace{2cm}\mbox{Rault's law pure}\\
  v_i' &= \frac{y_iP}{x_iK_i}\hspace{2cm}\mbox{Henry's law dilute}\\
\end{align*}

\begin{align*}
  \Delta T &= \frac{RT^2_{f/b}x_B}{\Delta H}\hspace{2cm}\mbox{Boiling/Freezing pt change}\\
  \Delta T &= \frac{RT^2_{f/b}m_Am_B}{\Delta H}\\
\end{align*}
